---
title: "Visualizations and aesthetics"
author: "Mitchell Dershowitz"
date: "6/12/2021"
output: html_document
---

## Step 1: Install and load the 'ggplot2' package and 'tidyverse' package


```{r loading and installing ggplot2, echo=FALSE, message=FALSE}
install.packages('ggplot2')
library(ggplot2)
library(tidyverse)
```

## Step 2: Making a Bar Chart

The bar chart below will summarize the distributions of hotel bookings to either city hotel or resort hotel.

```{r create bar chart}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel))
```

## Step 3: Exploring relationship between market_segment and deposit_type

Your stakeholder is interested in developing promotions based on different booking distributions, but first they need to know how many of the transactions are occurring for each different distribution type. Below are the bar plots that I created to present this information to the stakeholder.

```{r create bar chart}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_wrap(~market_segment) +
  theme(axis.text.x = element_text(angle = 45))

ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_grid(~deposit_type) +
  theme(axis.text.x = element_text(angle = 45))

ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = distribution_channel)) +
  facet_wrap(~deposit_type~market_segment) +
  theme(axis.text.x = element_text(angle = 45))
```


## Step 4: Family-Friendly promo between City Hotels and Resort Hotels

Now, your stakeholder wants to run a family-friendly promotion targeting key market segments. She wants to know which market segments generate the largest number of bookings, and where these bookings are made (city hotels or resort hotels). 

```{r bar chart}
ggplot(data = hotel_bookings) +
  geom_bar(mapping = aes(x = hotel)) +
  facet_wrap(~market_segment)
```

## Step 5: Filtering

After considering all the data, your stakeholder decides to send the promotion to families that make online bookings for city hotels. The online segment is the fastest growing segment, and families tend to spend more at city hotels than other types of guests. 

Your stakeholder asks if you can create a plot that shows the relationship between lead time and guests traveling with children for online bookings at city hotels. This will give her a better idea of the specific timing for the promotion. 

You think about it, and realize you have all the tools you need to fulfill the request. You break it down into the following two steps: 1) filtering your data; 2) plotting your filtered data. 

```{r filtering a dataset to just city hotels that are online TA}
onlineta_city_hotels <- filter(hotel_bookings, 
                           (hotel=="City Hotel" & 
                             hotel_bookings$market_segment=="Online TA"))
```

## Create Scatterplot using new filtered data frame

Based on your previous filter, this scatterplot shows data for online bookings for city hotels. The plot reveals that bookings with children tend to have a shorter lead time, and bookings with 3 children have a significantly shorter lead time (<200 days). So, promotions targeting families can be made closer to the valid booking dates.  

```{r creating a plot part two}
ggplot(data = onlineta_city_hotels) +
  geom_point(mapping = aes(x = lead_time, y = children))
```


